%% Tiago Fortunato CV
%% Updated 2026

\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\setlength{\footskip}{136.00005pt}
\linespread{1.06}

\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math}
\else
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\usepackage[english]{babel}

% Personal data
\name{Tiago}{Fortunato}
\title{\texorpdfstring{AI Application Engineer $|$ Product Engineer $|$ SaaS \\ {\small Founder of Odys · MSc Software Engineering · LLMs · RAG · Vision AI}}{AI Application Engineer | Product Engineer | SaaS | Founder of Odys | MSc Software Engineering | LLMs | RAG | Vision AI}}
\address{Berlin, Germany}
\phone[mobile]{+49~172~238~9909}
\email{tifortunato.eng@gmail.com}
\social[linkedin]{tiagorcfortunato}
\social[github]{tiagorcfortunato}
\homepage{tifortunato.com}

\begin{document}
\makecvtitle
\vspace{-3mm}

% -----------------------------------------------------------------------
\section{Profile}
% -----------------------------------------------------------------------
\cvitem{}{\textbf{AI Application Engineer} and \textbf{Product Engineer} in Berlin shipping \textbf{AI-powered products} end-to-end with \textbf{LLMs} and \textbf{RAG}. Founder of \textbf{Odys} (\href{https://odys.com.br}{odys.com.br}), a live \textbf{multi-tenant SaaS} built solo on Next.js, Stripe, and self-hosted WhatsApp. Built a production \textbf{RAG career chatbot} (\href{https://chatbot.tifortunato.com}{chatbot.tifortunato.com}) and a \textbf{Vision AI} REST API. \textbf{MSc Software Engineering} (Berlin 2026). Daily user of \textbf{Claude Code} and agentic AI workflows; my edge is shipping fast and owning outcomes from idea to production. \textbf{Trilingual}: Portuguese (native), English (fluent), German (B2.2). Open to \textbf{AI Application Engineer}, \textbf{Product Engineer}, AI Engineer, Solutions Engineer, or Founding Engineer roles.}

% -----------------------------------------------------------------------
\section{Skills}
% -----------------------------------------------------------------------
\cvitem{AI-Augmented Development}{\textbf{Claude Code}, Cursor, agentic coding workflows, prompt engineering. Daily user shipping production code with AI as a force multiplier.}
\cvitem{AI \& LLM Applications}{LLMs, RAG pipelines, embeddings, vector databases, LangChain, ChromaDB, Groq, Llama, Vision AI, LangSmith, RAGAs, fastembed, YOLOv8, PyTorch; hybrid retrieval (semantic + BM25), structured LLM output, evaluation, observability, streaming SSE.}
\cvitem{Backend \& APIs}{Python, FastAPI, REST APIs, PostgreSQL, SQL, SQLAlchemy, Drizzle ORM, Pydantic, Alembic, JWT auth, Pytest; clean architecture, schema design, and automated testing.}
\cvitem{Full-Stack \& SaaS}{TypeScript, JavaScript, React, Next.js, Tailwind, Supabase, Stripe, Resend, Upstash Redis; multi-tenant SaaS, subscription billing, transactional email, rate limiting, third-party integrations.}
\cvitem{DevOps \& Cloud}{Docker, GitHub Actions, CI/CD, AWS EC2, Nginx, Linux, Let's Encrypt, Railway, Vercel, Git; production deployments, containerization, and HTTPS-secured cloud infrastructure.}

% -----------------------------------------------------------------------
\section{Selected Projects}
% -----------------------------------------------------------------------

\cventry{2026--present}{Odys: Scheduling SaaS for Freelance Professionals}{Next.js 16 · TypeScript · Supabase · Stripe · Docker · Railway}{Berlin}{}{
WhatsApp-first SaaS platform where clients book online and receive automatic WhatsApp reminders; professionals manage availability, payments, and appointments from a dashboard. Live at \href{https://odys.com.br}{odys.com.br}.
\begin{itemize}
  \item Multi-tenant architecture: each professional gets a public booking page at \texttt{/p/[slug]} with fully isolated data and configurable availability
  \item Stripe subscriptions + PIX with webhook handling; Supabase Auth; Drizzle ORM on PostgreSQL; resolved PgBouncer transaction mode compatibility
  \item WhatsApp-native reminders via self-hosted Evolution API v2 on Railway, triggered by Supabase \texttt{pg\_cron} (not a third-party bot)
  \item Rate limiting with Upstash Redis; error monitoring with Sentry; transactional email via Resend; CI/CD via GitHub Actions
\end{itemize}}

\newpage

\cventry{2026}{AI Career Assistant: RAG Chatbot}{FastAPI · LangChain · ChromaDB · Groq · RAGAs · Docker · AWS EC2}{Berlin}{}{
Production RAG chatbot where recruiters ask questions about my background and get answers grounded in a curated knowledge base.
\begin{itemize}
  \item Hybrid retrieval: semantic search + BM25 fused with Reciprocal Rank Fusion; custom section-aware chunking
  \item Streaming SSE responses via Groq (Llama 3.1); RAGAs evaluation pipeline for retrieval quality
  \item Self-hosted on AWS EC2 with Docker, Nginx, and Let's Encrypt HTTPS. \href{https://chatbot.tifortunato.com}{chatbot.tifortunato.com} $|$ \href{https://github.com/tiagorcfortunato/ai-career-assistant}{GitHub}
\end{itemize}}

\cventry{2026}{Inspection Management API}{FastAPI · Groq Vision AI · LangChain · LangSmith · PostgreSQL · Docker}{Berlin}{}{
Production REST API that classifies inspection photos with Vision AI: upload an image and the system returns severity and damage type with explainable rationale.
\begin{itemize}
  \item Vision AI via Groq SDK; structured LLM output with LangChain; LangSmith for observability; XAI rationale field for transparency
  \item JWT auth with admin role; comprehensive Pytest suite covering all endpoints; CI/CD via GitHub Actions; frontend dashboard with image upload and AI status badges. \href{https://inspection-management-api.onrender.com/docs}{API Docs} $|$ \href{https://github.com/tiagorcfortunato/inspection-management-api}{GitHub}
\end{itemize}}

\cventry{2025--2026}{Road Hazard Detection \& Prioritization: MSc Thesis}{YOLOv8 · PyTorch · Python · RDD2022}{Berlin}{}{
Deep learning detection pipeline combined with a rule-based expert system for automated road maintenance prioritization on the RDD2022 dataset.
\begin{itemize}
  \item Best config (YOLOv8s): \textbf{mAP50 0.663, Precision 0.694, Recall 0.604}
  \item Rule-based post-processing reduced noisy detections by \textbf{31.2\%}; every prioritization decision traceable to explicit, auditable rules
\end{itemize}}

% -----------------------------------------------------------------------
\section{Experience}
% -----------------------------------------------------------------------

\cventry{2026--present}{Founder \& Full-Stack Developer}{Odys · \href{https://odys.com.br}{odys.com.br}}{Berlin, Germany}{}{
\begin{itemize}
  \item Identified a market gap: Brazilian freelance professionals losing time and money managing bookings manually via WhatsApp
  \item Owned the full product lifecycle as sole developer: market research, product design, technical architecture, implementation, and production deployment
  \item Product live and in active validation with industry professionals to refine product-market fit before scaling marketing
\end{itemize}}

\cventry{2019--2024}{Operations Manager}{Fortunato Joias, Family-Owned Jewelry Manufacturer}{Brazil}{}{Ran day-to-day operations of the family business: production planning, supplier relationships, and delivery cycles. Five years of end-to-end ownership before transitioning into software engineering full-time.}

\cventry{2018--2019}{Engineering Intern, Logistics \& Operations}{Metalúrgica Besser}{Rio de Janeiro, Brazil}{}{Supported logistics routines and production planning; reduced delays through structured problem solving.}

% -----------------------------------------------------------------------
\section{Education}
% -----------------------------------------------------------------------

\cventry{2024--2026}{MSc Software Engineering}{University of Europe for Applied Sciences}{Berlin, Germany}{}{}

\cventry{2014--2016}{Exchange Student, Mechanical Engineering}{Hochschule Wismar}{Germany}{}{}

\cventry{2013--2018}{BSc Mechanical Engineering}{UERJ}{Rio de Janeiro, Brazil}{}{}

% -----------------------------------------------------------------------
\section{Languages}
% -----------------------------------------------------------------------
\cvitem{}{Portuguese (Native) · English (Fluent) · German (B2.2)}

\end{document}
